InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

# return content between spaces
# pu things in the correct order
# library(stringr)
db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
unique(db_parsed$screencontent)
db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'

@@

# this might be needed for tempoal analisys
write_csv(db_parsed, 'db_parsed.csv')

@@

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')

db_parsed_summarised2$ssid<- as.numeric(db_parsed_summarised2$ssid)
db_parsed_summarised2
tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
rm(tmp.df4_sum_fullt)
testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)

tmp.df4_sum_fullt
```

@@

```{r}
colnames(X309_2019_Dec_11_1807_01)
library(data.table) 
library(purrr)

@@

# now read them
db_beh <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_plus_beh(.))

db328$condition<-db328$ï..condition

@@

# files <- list.files(pattern = ".csv")
# temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)

@@

>>>>

# return content between spaces
# put things in the correct order
library(stringr)

db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
unique(db_parsed$screencontent)
db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'

@@

# this might be needed for tempoal analisys
write_csv(db_parsed, 'db_parsed.csv')
write_csv(db_parsed, 'db_parsed_346_355.csv')

@@

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')

db_parsed_summarised2$ssid<- as.numeric(db_parsed_summarised2$ssid)
db_parsed_summarised2

# merge parsed with eyetracking data
# tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent")) #original

tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))

# rm(tmp.df4_sum_fullt)
# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
# 
# tmp.df4_sum_fullt
```

@@

```{r}
# colnames(X309_2019_Dec_11_1807_01)
library(data.table) 
library(purrr)

@@

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
# now read them
db_beh <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_plus_beh(.))

# problem file
# db328$condition<-db328$ï..condition

@@

files <- list.files(pattern = ".csv")
files
temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)

@@

etwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")

SC column = 2
Event marker column 3
sampling rate 150hz
